---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
#final code for report:
library(tidyverse)

latest_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vSmUPLB7jL4d00cEHQSpFoTLtxfo3ZRLe1480bfGlNWeD8Kydc1Iq17xGcqw2asaD5FViJUz545cV33/pub?output=csv") %>%
  rename(platform = 2,num_ads = 3, ads_interacted = 4,ads_relevant = 5, ad_repeated = 6)
 
```

```{css}
h2 {color: #14020D;font-size: 25px; font-family:lato}

body {background-color: #FFD1E4;font-family: Arial, sans-serif;
  font-size: 15px;}

```

##  Tracking Ad Exposure Across Social Media Platforms
This report analyses data collected from 20-minute social media sessions, tracking how many ads were seen, how many were interacted with, whether ads felt relevant, and whether any ad appeared more than once.
The data was collected across four platforms: YouTube, TikTok, Instagram, and Facebook.

 


```{r}

#mean number of ads
mean_ads <- mean(latest_data$num_ads)

#max number of ads
max_ads <- max(latest_data$num_ads)

#min number of ads
min_ads <- min(latest_data$num_ads)

#median number of ads
median_ads <- median(latest_data$num_ads)

#mean of ads interacted with
mean_interacted <-mean(latest_data$ads_interacted)

#max ads interacted with
max_interacted <- max(latest_data$ads_interacted)

#min ads interacted with
min_interacted <- min(latest_data$ads_interacted)

#median of ads interacted with
median_interacted <- median(latest_data$ads_interacted)


```
In a 20-minute social media session, participants saw an average of **`r mean_ads`** ads, 
with the number of ads ranging from **`r min_ads`** to **`r max_ads`**. 
On average, participants only interacted with **`r mean_interacted`** ads per session. 

```{r}
ggplot(data= latest_data) +
     geom_bar(aes(x= platform), fill = "plum") +
         labs(title = "Social Media Platforms Used in 20 Minute session", x= "Platform", y= "Count")

```

```{r}
ggplot(data = latest_data) +
     geom_bar(aes(x= num_ads), fill = "skyblue") +
         labs(title = "Number of Ads Seen in a 20 Minute Session", x= "Number of Ads", y= "Count")

```

```{r}
ggplot(data = latest_data) +
     geom_bar(aes(x= ads_interacted), fill = "hotpink")+
         labs(title = "Number of Ads Interacted With in a 20 Minute Social Media Break", x= "Amount Interacted With", y= "Count")

```


